\documentclass[11.5pt, letterpaper, roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{etaremune}
\usepackage{multicol}

\usepackage[margin=.90in]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

% Page Number
\usepackage{lastpage}
\pagestyle{fancy}
\fancyfoot[R]{\thepage\ / \pageref{LastPage}}


\firstname{Claire}
\familyname{Bowen}
\lfoot{CLAIRE MCKAY BOWEN}

\begin{document}
\vspace{-10pt}
\centerline{\huge{CLAIRE MCKAY BOWEN}}
\vspace{10pt}
\hrule
\vspace{8pt}
\centerline{\small Email: cbowen@urban.org | Website: \href{https://www.clairemckaybowen.com}{www.clairemckaybowen.com} | Last Updated: \today}
\vspace{8pt}
\hrule

\section{Education}
\cventry{}{Ph.D. Applied and Computational Mathematics and Statistics (ACMS)}{University of Notre Dame \textnormal{- Notre Dame, IN}}{\textnormal{\textit{May 2018}}}{}{
\underline{Advisor}: \href{http://acms.nd.edu/people/faculty/fang-liu/}{Dr. Fang Liu}\\
\underline{Dissertation Topic}: Data Privacy via Integration of Differential Privacy and Data Synthesis}

\vspace{4pt}
\cventry{}{M.S. Applied and Computational Mathematics and Statistics | GPA: 3.91/4.00}{University of Notre Dame \textnormal{- Notre Dame, IN}}{\textnormal{\textit{May 2015}}}{}{}

\vspace{4pt}
\cventry{}{Honors B.S. Mathematics and Physics | Minor: Statistics | High Honors: Top 5\% | GPA: 3.94/4.00}{Idaho State University \textnormal{- Pocatello, ID}}{\textnormal{\hspace{-25pt}\textit{Dec. 2012}}}{}{}

\section{Professional Experience}
\cventry{}{Lead Data Scientist, Privacy and Data Security}{Urban Institute}{\textnormal{\textit{Dec. 2019 - Present}}}{}{
    \begin{itemize}
        \item Co-leading a multi-year project with the IRS to create synthetic versions of the income tax return database, assess the quality and privacy guarantee of the generated synthetic data, and develop methods for researchers to access confidential administrative data safely and securely.
        \item Managing a data privacy project on generating synthetic data on employer and employee industry data in rural communities in collaboration with the Bureau of Labor Statistics.
        \item Creating and designing an interactive dashboard to assess and evaluate the 2020 Decennial Census population results in collaboration with Georgetown University.
        \item Developing a body of work on data privacy and confidentiality communications.
    \end{itemize}}

\vspace{4pt}
\cventry{}{Postdoctoral Research Associate}{Los Alamos National Laboratory (LANL) - Los Alamos, NM}{\textnormal{\textit{\hspace{-1cm}June 2018 - Dec. 2019}}}{}
{\underline{Advisors}: Dr. Joanne Wendelberger and Dr. Earl Lawrence
\begin{itemize}
    \item Evaluate various differentially private data synthesis methods and quality metric algorithms to assess practical applications.
    \item Develop new methods of functional data analysis and human-in-the-loop for iterative design.
    \item Investigate the reliability of computer hardware such as cosmic ray effects on supercomputers e.g. Trinity.
    \item Analyze Texas Pre-K to college longitudinal education data to identify attributes for success.
    % \item Explore and improve component reliability modeling within a Bayesian Framework.
\end{itemize}}

\vspace{4pt}
\cventry{}{Graduate Research Assistant }{U.S. Census Bureau - Suitland, MD}{\textnormal{\textit{Aug. 2016 - Oct. 2016}}}{}
{\underline{Mentors}: Dr. Tommy Wright and Dr. Martin Klein
\begin{itemize}
\item Implemented methods of data privacy and confidentiality to U.S. Census Bureau data; specifically, applying model-based differentially private data synthesis methods.
\end{itemize}}

\vspace{4pt}
\cventry{}{Graduate Research Assistant}{Los Alamos National Laboratory (LANL) - Los Alamos, NM}{\textnormal{\textit{May 2015 - July 2015}}}{}
{\underline{Mentors}:  \href{http://www.lanl.gov/expertise/profiles/view/joanne-wendelberger}{Dr. Joanne Wendelberger} and \href{http://www.lanl.gov/expertise/profiles/view/lawrence-ticknor}{Mr. Lawrence Ticknor}
\begin{itemize}
\item Improved an in situ method for approximating complex computer simulations, resulting in a publication.
\item Created a R package and Shiny App of the developed method as additional learning tools for researchers.
\end{itemize}}

\vspace{4pt}
\cventry{}{Probability and Statistics Instructor}{University of Notre Dame - Notre Dame, IN, Dept. of ACMS}{\textnormal{\textit{Jan. 2015 - May 2015}}}{}{
\begin{itemize}
\item Teaching duties included preparing a syllabus, lecturing, assigning homework, writing exams, and holding weekly office hours.
%\begin{itemize}
%\item \textbf{Spring 2015:} Probability and Statistics for Computer Scientists and Engineers
%\end{itemize}
\end{itemize}}

\section{Publications}
% \noindent Citation counts found via Google Scholar and Research Gate.\\
% \hspace{0in}\noindent\underline{\textbf{To Appear}}

\noindent\underline{\textbf{Refereed Publications}}
\vspace{4pt}
\begin{etaremune}[topsep=0pt, itemsep=8pt, partopsep=0pt, parsep=0pt]
    \item \textbf{Bowen, CMK.}, Liu, F., Su, B. (2021) ``Differentially Private Data Release via Statistical Election to Partition Sequentially.'' \textit{to appear in METRON}
    (arXiv:1803.06763)
    
    \item \textbf{Bowen, CMK.} and Snoke, J. (2021) ``Comparative Study of Differentially Private Synthetic Data Algorithms from the NIST PSCR Differential Privacy Synthetic Data Challenge.'' \textit{Journal of Privacy and Confidentiality}, 11 (1).\\
    doi: 10.29012/jpc.748
    
    \item Snoke, J., and \textbf{Bowen, CMK.} (2020) ``How Statisticians Should Grapple with Privacy in a Changing Data Landscape.'' \textit{CHANCE}, 33(4), 6-13.\\
    doi: 10.1080/09332480.2020.1847947
    
    \item \textbf{Bowen, CMK.}, Bryant, V., Burman, L., Khitatrakun, S., McClelland, R., Stallworth, P., Ueyama, K., Williams, A. (2020) ``A Synthetic Supplemental Public Use File of Low-Income Information Return Data: Methodology, Utility, and Privacy Implications.'' \textit{International Conference on Privacy in Statistical Databases} (pp. 257-270). Springer, Cham.
    
    \item Liu, F., Eugenio, E., Jin, I., and \textbf{Bowen, CMK}. (2020) ``Differentially Private Generation of Social Networks via Exponential Random Graph Models.'' \textit{Proceedings of 2020 IEEE 44th Annual Computers, Software, and Applications Conference (COMPSAC)}, Pages:1695-1700.\\
    doi: 10.1109/COMPSAC48688.2020

    \item \textbf{Bowen, CMK.} and Liu, F. (2020) ``Comparative Study of Differentially Private Data Synthesis Methods.'' \textit{Statistical Science}, 35(2):280-307.

    \item \textbf{Bowen, CMK.}, DeBardeleben, N., Blanchard, S., Anderson-Cook, C. (2019) ``Do Solar Proton Events Reduce the Number of Faults in Supercomputers?: A Comparative Analysis of Faults during and without Solar Proton Events." \textit{2019 IEEE International Reliability Physics Symposium}.

    \item \textbf{Bowen, CMK.} and Eugenio, E. (2017) ``Where's Wenda:  An Activity on Teaching Middle School Students Data Privacy.'' \textit{Statistics Teacher}, Issue No. 1.
    
    \item Myers, K., Lawrence, E., Fugate, M., \textbf{Bowen, CMK.}, Ticknor, L., Woodring, J., Wendelberger, J., Ahrens, J. (2016) ``Partitioning a Large Simulation as It Runs.'' \textit{Technometrics}, Volume 58, Issue 3, 329-340. \\
    doi: 10.1080/00401706.2016.1158740
    % \textbf{Citations:} 12

    \item \textbf{Bowen, CMK.}, Liu, F., \& Wheeler, J. (2015) ``Are More of My Patients Developing Side Effects than Expected.'' \textit{Practical Radiation Oncology}, Volume 5, Issue 3, e255-e261.\\
    doi: 10.1016/j.prro.2014.10.007
    
% \vspace{4pt}
% \hspace{-0.30in}\noindent\underline{\textbf{Under Review/Preprint}}
%     \item \textbf{Bowen, CMK.}, Liu, F., Su, B. (2018) ``Differentially Private Data Release via Statistical Election to Partition Sequentially.''
%     (arXiv:1803.06763)
\end{etaremune}

\vspace{8pt}
\noindent\underline{\textbf{Books}}

\begin{etaremune}[topsep=0pt, itemsep=8pt, partopsep=0pt, parsep=0pt]
  \item \textbf{Bowen, CMK.} ``Public Trust: Protecting Your Privacy with Statistics in a World Driven by Data.'' \textit{in preparation}.
\end{etaremune}

\vspace{8pt}
\noindent\underline{\textbf{Non-Refereed Publications}}

\begin{etaremune}[topsep=0pt, itemsep=8pt, partopsep=0pt, parsep=0pt]
    \item Brown, S, MacDonald, G., and \textbf{Bowen, CMK.} (2021) ``How the Federal Government Can Use Data to Make the Most of the Executive Order on Racial Equity.'' \textit{Urban Wire}. 

    \item \textbf{Bowen, CMK.}, Narayanan, A., Scally, C. (2021) ``Using Differential Privacy to Advance Rural Economic Development: Applying Data Privacy and Confidentiality Methods to Industry Employment Data.'' \textit{Urban Institute}

    \item \textbf{Bowen, CMK.} (2020) ``To bike or not to bike...in a group?'' \textit{International Statistical Institute}, Statisticians React to the News.

    \item \textbf{Bowen, CMK.} (2020) ``My ASA Story.'' \textit{Amstat News}, December Issue.

    \item Chase, E., \textbf{Bowen, CMK.}, Director, H., Baladandayuthapani, V. and Pierson, S. (2020) ``Panel Shares Advice on Applying for NSF Fellowships.'' \textit{Amstat News}, November Issue.

    \item \textbf{Bowen, CMK.}, Burman, L., Khitatrakun, S., MacDonald, G., McClelland, R., Stallworth, P., Ueyama, K., Williams, A., Zwiefel, N. (2020) ``A Synthetic Supplemental Public-Use File of Low-Income Information Return Data: Methodology, Utility, and Privacy Implications.'' \textit{Urban Institute}

    \item \textbf{Bowen, CMK.} and Mannshardt, E. (2020) ``Committee on Career Development Holds Virtual Office Hours with Experts.'' \textit{STAT tr@k News}, June Issue.

    \item \textbf{Bowen, CMK.} and Mannshardt, E. (2020) ``Reaching Your Networking Peak: A Guided Networking Session at JSM.'' \textit{Amstat News}, April Issue.
    
    \item \textbf{Bowen, CMK.} (2020) ``Will the Census Bureau's data privacy efforts erase rural America?'' \textit{Urban Wire}. 
    
    \item Snoke, J. and \textbf{Bowen, CMK.} (2019) ``Differential Privacy: What Is It?'' \textit{Amstat News}, March Issue.
    
    \item \textbf{Bowen, CMK.} (2016) ``NSF GRIP Report: American Community Survey Simulation Study." \textit{U.S. Census Bureau}.  
\end{etaremune}

\section{Recent Invited Presentations}
\begin{etaremune}[topsep=0pt, itemsep=8pt, partopsep=0pt, parsep=0pt]
\smallskip
    \item Aug. 2021. \textit{Another Invisible Threat: Unequal Privacy Cost of Tracing COVID-19}. Joint Statistical Meetings at Seattle, WA. \textbf{Will be presenting.}
    
    \item Feb. 2021. \textit{How Statistics Protects Your Privacy in a World Driven by Data}. STEM Seminar Series, Henderson State University, Virtual.

    \item Nov. 2020. \textit{Data Privacy in the Real World}. Statistics Seminar Series, Bureau of Labor Statistics, Virtual.

    \item Sept. 2020. \textit{Data Privacy in the Real World}. Statistics Seminar Series, University of Pittsburgh, Virtual.

    \item June 2020. \textit{Telling a Visual Story in Big Data: Case Studies on Interactive Visualizations for Supercomputer Data}. Symposium on Data Science and Statistics, Virtual.
  
    \item June 2020. \textit{Best Practices for Leading DS Efforts in Your Organization}. Symposium on Data Science and Statistics, Virtual.  
    
    \item April 2020. \textit{Differential Privacy: What is it?} Women in Data Science Conference, the Virginia Tech at Blacksburg, VA.
    
     \item Feb. 2020. \textit{Comparative Study of Differentially Private Synthetic Data Algorithms and Evaluation Standards}. Statistics Colloquia, University of California-Riverside at Riverside, CA.
  
    \item Feb. 2020. \textit{How to Tell a Less Flawed Data Story: Data Analytics, Data Communication, and Data Privacy}. Statistics Seminar, Bryant University at Provenance, RD.
  
\end{etaremune}

\newpage
\section{Grants \& Fellowships}
    \vspace{4pt}
    \cventry{}{Economic Institutions, Behavior, and Performance | \$400,000}{Alfred P. Sloan Foundation}{\textnormal{\textit{Nov. 2020 - Oct. 2022}}}{}{
    \underline{Project:} 
    Development and Deployment of a Prototype Validation Server for Administrative Tax Data\\
    \underline{PI:} Claire McKay Bowen\\
    \underline{Co-PIs:} Leonard Burman and Graham MacDonald
    }
    
    \vspace{4pt}
    \cventry{}{Tableau Foundation | \$470,000}{Tableau and Salesforce}{\textnormal{\textit{Jan. 2021 - Oct. 2021}}}{}{
    \underline{Project:} Decennial Dashboard\\
    \underline{PI:} Claire McKay Bowen\\
    \underline{Co-PIs:} Amy O'Hara
    }

    \vspace{4pt}
    \cventry{}{NSF National Center for Science and Engineering Statistics | \$600,000}{National Science Foundation}{\textnormal{\textit{Oct. 2020 - Sept. 2021}}}{}{
    \underline{Project:} Planning and Development of a Prototype Privacy-Preserving Validation Server for Administrative Tax Data\\
    \underline{PI:} Claire McKay Bowen\\
    \underline{Co-PIs:} Leonard Burman and Graham MacDonald
    }
    
    \vspace{4pt}
    \cventry{}{South Big Data Hub | \$50,000}{South Big Data Hub Seed Grant}{\textnormal{\textit{Jan. 2021 - July 2021}}}{}{
    \underline{Project:} Data4Kids: Virtually Teaching Kids about Data Science\\
    \underline{PIs:} Jonathan Schwabish\\
    \underline{Co-PI:} Claire McKay Bowen
    }
    
    % \vspace{4pt}
    % \cventry{}{Urban Institute | \$25,000}{Fleishman Innovation Award}{\textnormal{\textit{May 2020 - Dec. 2020}}}{}{
    % \underline{Project:} Optimizing Data to Advance Rural Economic Development\\
    % \underline{PI:} Claire McKay Bowen\\
    % \underline{Co-PIs:} Corianne Scally and Ajjit Narayanan
    % }

    \vspace{4pt}
    \cventry{}{NIST Public Safety Communications Research | \$100,000}{National Institute of Standards and Technology (NIST)}{\textnormal{\textit{Oct. 2019 - Jan. 2020}}}{}{
    \underline{Project:} Comparative Study of Differentially Private Synthetic Data Algorithms and Evaluation Standards\\
    \underline{PIs:} Claire McKay Bowen
    }
    
    % \vspace{2pt}
    % \cventry{}{University of Notre Dame John J. Reilly Center | \$5,000}{Reilly Center Mini-Grant}{\textnormal{\textit{July 2016}}}{}{
    % \underline{Project:} Regional Women in Science Conference\\
    % \underline{Co-PIs:} Suzanne Neidhart and Claire McKay Bowen
    % }

    % \vspace{4pt}
    % \cventry{}{National Science Foundation | \$5,000}{National Science Foundation Graduate Research Internship Program}{\textnormal{\textit{May 2016}}}{}{}

    \vspace{4pt}
    \cventry{}{National Science Foundation | Grant No. DGE-1313583 | \$138,000}{National Science Foundation Graduate Research Fellowship}{\textnormal{\textit{May 2015}}}{}{}
    
    \vspace{4pt}
    \cventry{}{Microsoft | \$17,000}{Microsoft Graduate Women's Fellowship}{\textnormal{\textit{Feb. 2014}}}{}{}

\section{Service}

\underline{\textbf{\large Editorial}}\normalsize

\textbf{Journal, Conference Proceeding, and Book Referee for:}\\
The American Statistician, CRC Press, ACM-IMS Foundations of Data Science, Journal of Privacy and Confidentiality, Journal of Royal Statistical Society - Series A, Journal of Survey Statistics and Methodology, WSDS: PrivateNLP, Quality Engineering

\vspace{12pt}
\underline{\textbf{\large National Leadership}}\normalsize

\cventry{}{}{American Statistical Association}{\textnormal{\textit{Jan. 2020 - Present}}}{}{
    \vspace{-12pt}
    Program Chair for the Section on Statistics in the Physical \& Engineering Sciences \hfill2020 - 2022\\
    Secretary/Treasurer for the Section on Statistical Computing \hfill 2020 - 2021\\
    Committee on Career Development \hfill 2019 - 2021
    \begin{itemize}
        \item Vice-Chair \hfill 2020
        \item Chair \hfill 2021
    \end{itemize}
}

\end{document}
